Clustering

### 2016-03-23 scrap/clustering.rmd
r and v can be fixed

@@

pamk_clusters <- ddply(exp_1000, .variables = .(patch_area), 
          .fun = function (df){
            m <- pamk(df$e_0, krange = 1:3, alpha = 1e-12)
            cluster <- m$pamobject$clustering
            mediod <- m$pamobject$medoids[cluster]
            distance <- m$pamobject$clusinfo[cluster, "diameter"]
            nc <- max(cluster)
            unique(data.frame(cluster, mediod, distance, nc))
          })

ggplot(pamk_clusters, aes(x = patch_area, y = mediod)) +
  geom_errorbar(aes( ymin = mediod - (distance/2), ymax = mediod + (distance/2))) +
  geom_point(aes(col=as.factor(nc))) + 
  ylab("log(beta)") + 
  ggtitle("Clustered using pamk") + 
  scale_colour_discrete(name="Number of Clusters")

@@

qplot(data = exp_1000, mass, fill=as.factor(patch_area), main ="mass distrobution of winners, mass center of inital population is 4")

qplot(data = exp_1000, x = patch_area, y = mass)

>>>>

cm_6k <- load_population("~/Documents/contests_model/data/cm_100/")
clustered_plot(cm_6k, what = "e_0", ylab = "beta")

@@

pamk_clusters <- ddply(exp_100, .variables = .(patch_area), 
          .fun = function (df){
            c1 <- pamk(df$k, krange = 1:3, alpha = 1e-12)
            k_cluster <- c1$pamobject$clustering
            k_mediod <- c1$pamobject$medoids[k_cluster]
            k_distance <- c1$pamobject$clusinfo[k_cluster, "diameter"]
            k_nc <- max(k_cluster)

            c2 <- pamk(df$e_0, krange = 1:3, alpha = 1e-12)
            e_0_cluster <- c2$pamobject$clustering
            e_0_mediod <- c2$pamobject$medoids[e_0_cluster]
            e_0_distance <- c2$pamobject$clusinfo[e_0_cluster, "diameter"]
            e_0_nc <- max(e_0_cluster)

            data.frame(k_cluster, k_mediod, k_distance, k_nc, e_0_cluster, e_0_mediod, e_0_distance, e_0_nc)
          })

ggplot(data = pamk_clusters, aes(x = patch_area)) + 
  geom_point(aes(y = k_nc, col = as.factor(e_0_nc)))

pamk_1000 <- pamk_clusters[pamk_clusters$patch_area == 1000, ]

ggplot(data = exp_100[exp_100$patch_area == 1000, ], aes(x = k)) + 
  geom_point(aes(y = e_0))
  geom_polygon

ggplot(pamk_clusters, aes(x = patch_area, y = mediod)) +
  geom_errorbar(aes( ymin = mediod - (distance/2), ymax = mediod + (distance/2))) +
  geom_point(aes(col=as.factor(nc))) + 
  ylab("beta") + 
  ggtitle("Clustered using pamk") + 
  scale_colour_discrete(name="Number of Clusters")

@@

pamk(exp_100[exp_100$patch_area == 4600,]$k, krange = 1:3, alpha = 1e-12)
